PWD.KAZ

### 2019-07-16 results/PWD.KAZ.BivData.Rmd
adding more data to slides

SC.KAZ <- ggplot(data = KAZ_curate_BivData, aes(color=fileName,x=mouse, y= chromosomeLength))+geom_jitter()+theme(legend.position="none")+ylim(c(35,150))+ggtitle("KAZ SC lengths")
#can I add the means?

SC.PWD
SC.KAZ
```

```{r cell.tables}
#add total COs
KAZ_BivData_cells <- ddply(KAZ_curate_BivData, c("fileName"), summarise,

@@

bin.short.PWD <- DF.w.rank2[DF.w.rank2$rank < 5,]
bin.short.PWD <- bin.short.PWD[bin.short.PWD$fileName %in% full.cell.list$fileName,]

kk <- ggplot(data=bin.short.PWD, aes(x=fileName,y=chromosomeLength))+geom_jitter(width = 0.25, aes(color =Foci1, shape=mouse))+ggtitle("short bins")

@@

```{r}
#histograms to display the average number of Objects per cell
PWD.curateautoBivData_cells <- ddply(PWD_curate_BivData, c("fileName"), summarise,
                    number = length(Obj.ID)

@@

@@

```{r}
#proportions of bivalent classes
foci.passed.KAZ <- curBivData_KAZ[curBivData_KAZ$foci.pass == 1,]

foci.passed.PWD <- curBivData_PWD[curBivData_PWD$foci.pass == 1,]

qq <- ggplot(data = foci.passed.KAZ, aes(color=fileName,x=mouse, y= hand.foci.count))+geom_jitter()+theme(legend.position="none")

#PWD have more 2CO bivalents

>>>>

SC.KAZ <- ggplot(data = KAZ_curate_BivData, aes(color=fileName,x=mouse, y= chromosomeLength))+geom_jitter()+
  theme(legend.position="none")+ylim(c(35,150))+ggtitle("KAZ SC lengths")
#can I add the means?

SC.PWD
SC.KAZ

KAZ_mean_SC <- ddply(KAZ_curate_BivData, c("mouse"), summarise,

                    avSC.length = mean(chromosomeLength),
                    varSC.length = var(chromosomeLength)
)

PWD_mean_SC <- ddply(PWD_curate_BivData, c("mouse"), summarise,

                    avSC.length = mean(chromosomeLength),
                    varSC.length = var(chromosomeLength)
)

t.test(KAZ_curate_BivData$chromosomeLength,PWD_curate_BivData$chromosomeLength)

the PWD has longer means

```{r SClength.cell.tables}
#add total COs
KAZ_BivData_cells <- ddply(KAZ_curate_BivData, c("fileName"), summarise,

@@

bin.short.PWD <- PWD_whole.cell.BivData[PWD_whole.cell.BivData$rank < 5,]

bin.short.PWD <- bin.short.PWD[bin.short.PWD$fileName %in% full.cell.list$fileName,]

kk <- ggplot(data=bin.short.PWD, aes(x=mouse,y=chromosomeLength))+geom_jitter(width = 0.25)+ggtitle("short bins")

@@

```{r hist.boxes.per.cell, echo=FALSE}
#histograms to display the average number of Objects per cell
PWD.curateautoBivData_cells <- ddply(PWD_curate_BivData, c("fileName"), summarise,
                    number = length(Obj.ID)

@@

```{r SC.by.bins}

all.whole.cell <- rbind(KAZ_whole.cell.BivData,PWD_whole.cell.BivData)

#compare short and long bins
bin_short <- all.whole.cell[all.whole.cell$rank < 5,]

bin_short <- all.whole.cell[all.whole.cell$rank < 3,]#comparing the bottom 3 are not sig different

#bin.short.PWD <- bin.short.PWD[bin.short.PWD$fileName %in% full.cell.list$fileName,]

short_SC <- ggplot(data=bin_short, aes(x=mouse,y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=fileName))+ggtitle("short bins")+facet_wrap(~strain)+ theme(legend.position="none")

t.test(bin_short$chromosomeLength[bin_short$strain == "PWD"],
       bin_short$chromosomeLength[bin_short$strain == "KAZ"])

#p-value = 0.02131

bin_long <- all.whole.cell[all.whole.cell$rank > 15,]#comparing the top 3 is not sig different

long_SC <- ggplot(data=bin_long, aes(x=mouse,y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=fileName) )+ggtitle("Long bins")+facet_wrap(~strain)+ theme(legend.position="none")

t.test(bin_long$chromosomeLength[bin_long$strain == "PWD"],
       bin_long$chromosomeLength[bin_long$strain == "KAZ"])

#p-value = 0.01495
```

```{r chrm.class, echo=FALSE}
#proportions of bivalent classes

foci.passed.KAZ <- KAZ_curate_BivData[KAZ_curate_BivData$foci.pass == 1,]
foci.passed.PWD <- PWD_curate_BivData[PWD_curate_BivData$foci.pass == 1,]

jj <- rbind(foci.passed.KAZ,foci.passed.PWD)

qq <- ggplot(data = jj, aes(color=fileName,x=mouse, y= hand.foci.count))+geom_jitter()+theme(legend.position="none")+facet_wrap(~strain)

#PWD have more 2CO bivalents
biv_class_table <- ddply(jj, c("hand.foci.count", "strain"), summarise,
                    number = length(Obj.ID)
)

#### use whole cell data

KAZ_whole.cell.BivData
all.whole.cell
#chi-squard test?

whole.cell_biv_class_table <- ddply(all.whole.cell, c("hand.foci.count", "strain"), summarise,
                    number = length(Obj.ID)
)

@@
